04_DESeq_sexes

### 2019-08-28 analysis/04_DESeq2_sexes.Rmd
werid FALSE is everywhere

```{r setup, include = FALSE}

@@

# set levels
c.colData$treatment <- factor(c.colData$treatment, levels = 
                              c("control",  "bldg", "lay", "inc.d3", "inc.d9", "inc.d17", "hatch", "n5", "n9"))

c.colData$sextissue <- as.factor(paste(c.colData$sex, c.colData$tissue, sep = "_"))

c.colData <- c.colData %>%
    mutate(hypothesis = fct_recode(treatment,
                            "anticipation" = "control",
                            "anticipation" = "bldg",
                            "incubation" = "lay",
                            "incubation" = "inc.d3",
                            "incubation" = "inc.d9",
                            "incubation" = "inc.d17",
                            "hatchling.care" = "hatch",
                            "hatchling.care" = "n5",
                            "hatchling.care" = "n9"))

>>>>

```{r setup}

@@

# set treatment levels
c.colData$treatment <- factor(c.colData$treatment, levels = 
                              c("control",  "bldg", "lay", "inc.d3", "inc.d9", "inc.d17", "hatch", "n5", "n9"))

# craete variable that will be critical for subset later on
c.colData$sextissue <- as.factor(paste(c.colData$sex, c.colData$tissue, sep = "_"))

# ceate new variable for hypothesis testing
c.colData <- c.colData %>%
    mutate(hypothesis = fct_recode(treatment,
                            "anticipation" = "control",
                            "anticipation" = "bldg",
                            "incubation" = "lay",
                            "incubation" = "inc.d3",
                            "incubation" = "inc.d9",
                            "incubation" = "inc.d17",
                            "hatchling.care" = "hatch",
                            "hatchling.care" = "n5",
                            "hatchling.care" = "n9"))
